|

### 2021-08-01 dissertation/msc_dissertation.Rmd
Updating scripts

 @silberzahn2018 and @botvinik-nezer2020 suggest using multiverse analysis strategies (also known as specification-curve analysis) to get a more accurate representation of the results space. This analytical strategy refers to conducting analyses for all "reasonable specifications" (or at least a large sample thereof). "Reasonably" is defined as statistically valid tests, scrutinising the research question and non-redundant[@simonsohn2020].

@patel2015

>>>>

 @silberzahn2018 and @botvinik-nezer2020 suggest using multiverse analysis strategies (also known as specification-curve analysis) to get a more accurate representation of the results space. This analytical strategy refers to conducting analyses for all "reasonable specifications" (or at least a large sample thereof). "Reasonably" is defined as statistically valid tests, scrutinising the research question and non-redundant [@simonsohn2020]. The idea is to simulate a 
Vibration of effect @patel2015

The present study will build upon @silberzahn2018, @botvinik-nezer2020 and @patel2015. It has been established that results vary and
